\subsection{{\href{https://www.insabhi.com}{Insabhi Project's} \hfill}}
{\color{black}%
\begin{itemize}[itemsep=0.1em, parsep=0pt, topsep=0pt]
\item Developed an \textbf{auto-blogging system} that analyzes content from users’ websites to generate blog posts on a custom \textbf{subdomain} or via \textbf{iframe} integration for seamless embedding.
\item Led the complete design and customization of the \href{https://chillopositefestival.com/}{\textbf{Chilloposite}} website, including ordering and user interface features tailored for festival management.
\item Built and deployed the official \textbf{Batissure} website, focusing on clean design, performance optimization, and responsive layout.
\item Integrated and customized \textbf{Kitchen POS} within \textbf{Odoo ERP}, adding advanced features like discounts, streamlined workflows, and order processing enhancements.
\item Contributed to major client projects like \href{https://falcann.com/}{\textbf{Falcann}} and \textbf{Amicco}, delivering tailored ERP and web solutions to meet unique business needs.
\item Collaborated on multiple other internal and client-focused web and ERP modules under tight deadlines.
\end{itemize}%
}


\subsection{{Freelancing Project's \hfill }}
{\color{black}%
\begin{itemize}[itemsep=0.1em, parsep=0pt, topsep=0pt]
\item Built a comprehensive \href{https://ujjwal-dresses.onrender.com/}{\textbf{Product Management System}} using \textbf{MongoDB}, \textbf{Express}, \textbf{React}, and \textbf{Node.js}, featuring advanced middleware, custom APIs, and robust CRUD functionality.
\item Developed \href{https://journey-junction-hy4h.onrender.com/}{\textbf{Journey Junction}} — a full-featured \textbf{trip planning and booking platform} — along with an \href{https://journey-junction-admin-react.onrender.com}{\textbf{admin dashboard}}, leveraging the MERN stack with role-based access control and dynamic trip management.
\item Created a highly interactive \textbf{3D Panorama Viewer} for a photo studio, enhancing user experience through immersive visual navigation.
\item Delivered multiple end-to-end freelance solutions, ensuring responsive design, optimized performance, and seamless client integration.
\end{itemize}%
}

